Associahedra for finite type cluster algebras \\ and minimal relations between $\b{g}$-vectors

### 2019-07-09 thirdPaper/draft/typeConeAssociahedra.tex
3 typos

In \cref{sec:clusterCategories}, we prove an analogue for cluster categories of M. Auslander's result~\cite{Auslander1984}.
We are mainly motivated by the fact that itt has for a consequence that the type cones of the cluster fans of finite type are simplicial.
However, this result is of independent interest and sheds new lights on the Grothendieck groups of cluster categories.

@@

The previous two statements also hold when~$T$ is an additive subcategory rather than a mere object.
Assume moreover that~$\cat$ is~$\field$-linear, Ext-finite, Krull--Schmidt and has Auslander--Reiten--Serre duality.
Then, with notations analoguous to those used for cluster categories above, we obtain the following:

>>>>

In \cref{sec:clusterCategories}, we prove an analogue for cluster categories of M. Auslander's result~\cite{Auslander1984}.
We are mainly motivated by the fact that it has for a consequence that the type cones of the cluster fans of finite type are simplicial.
However, this result is of independent interest and sheds a new light on the Grothendieck groups of cluster categories.

@@

The previous two statements also hold when~$T$ is an additive subcategory rather than a mere object.
Assume moreover that~$\cat$ is~$\field$-linear, Ext-finite, Krull--Schmidt and has Auslander--Reiten--Serre duality.
Then, with notations analogous to those used for cluster categories above, we obtain the following:
